Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex
alex

Our comparison of Python mutation tools showed the largest degree of
similarity between all tools.  Mutation scores and equivalence rates
were all, given the large variance expected from previous studies of
Java tools, quite similar.  Again, there is no clear disadvantage to
using our approach, and a large advantage in terms of development and
maintenance ease.  Comby had a somewhat higher equivalence rate than the
other tools (including the Regexp mode of our tool).  We discuss
possible reasons for this below.

>>>>

Our comparison of Python mutation tools again showed that there is no
evident disadvantage to
using our approach, in terms of mutation testing results.  Comby had a somewhat higher mean equivalence rate than the
other tools (including the Regexp mode of our tool), but with one
exception still achieved a very good equivalence rate.  Again, discarding
equivalent mutants, our tool produced more mutants, and more unkilled
mutants, than other tools, but still had a similar overall mutation
score (the only clear outlier in scores is Mutmut's high score for the
keract project).  We discuss
possible reasons for higher Comby equivalence rates below.
